The Forward March of Categorical Tolerance in the United States\thanks{Reserved for acknowledgments}

### 2025-11-14 manuscript.tex

\newpage
\begin{abstract}
This paper updates the empirical picture of Categorical Tolerance (CT), namely, the pattern of refusing to report dislikes across cultural genres, in the United States during the third decade of the twenty-first century. Analyzing recent survey data from two platforms, I find that CT has continued its march among Americans, reaching approximately 20\% of respondents. The analysis confirms the persistence of earlier-observed demographic trends, showing that CT is strongly associated with younger cohorts and non-white individuals. However, I also find that individuals reporting the highest educational attainment are now overrepresented among categorical tolerants, suggesting that CT may increasingly function as an elite cultural strategy consistent with contemporary forms of status display, signaling openness and refusal to refuse. Furthermore, the study uses political ideology as a predictor of symbolic exclusion, revealing that while the odds of being a CT itself are not strongly polarized, the inclination toward symbolic exclusion among non-CTs is, with conservatives significantly more likely to express a greater volume of cultural dislikes than liberals. This result shows that political ideology, alongside age and race, is a central determinant of cultural exclusion in the contemporary context. 
\end{abstract}
\newpage
\section*{Introduction}
Ever since Richard Peterson introduced the felicitous term ``patterns of cultural choice'' into sociological discourse more than four decades ago \citep{peterson1983patterns-f85}, sociologists have been busy empirically uncovering and debating the sociological reality, drivers, and correlates of various such patterns. These include, most famously and influentially, the Petersonian cultural \textit{omnivore} \citep{peterson1996changing-967, goldberg2011mapping-77a, warde2008omnivorous-e77} along with their evil twin the culturally exclusive \textit{univore} \citep{bryson1997what-933, peterson1992understanding-ce3, tonkovi2025globallocal-96f}, but also culturally \textit{voracious} consumers \citep{sullivan2007omnivore-018}, \textit{poly-purists} and \textit{poly-mixers} \citep{goldberg2016what-4e3, poecke2018pure-873}, \textit{decisives} and \textit{indecisives} \citep{sonnett2004musical-961}, and even plain old \textit{snobs} engaging in (presumably) Bourdieusian boundary-drawing distinction \citep{atkinson2011context-d44, nault2021social-1bf}, among many others.

@@

Why are dislikes expressed in social surveys on cultural tastes important? As \citet{bourdieu1984distinction-835} himself noted, taste is often asserted negatively through refusal (p. 56). \citet{bryson1996anything-311} linked this dynamic to the idea of ``symbolic exclusion'' or the \textit{indirect} action of drawing a symbolic (social) boundary against particular (usually lower status) groups by distancing oneself from the cultural objects that those groups are perceived to consume \citep{lizardo2016cultural-aaa}. This recognition has led scholars to stress the critical importance of studying ``dislikes" alongside ``likes" to fully comprehend the dynamics of symbolic exclusion and the construction of cultural boundaries \citep{lizardo2015musical-8c6, lindblom2022growing-ded, oncini2023cultural-323}. This general framework has proven helpful for understanding social and cultural dynamics, even beyond the case of the United States. For example, a recent study of musical taste conducted in South Korea found that tolerant omnivores still excluded genres like ``gugak" (Korean traditional music) and ``trot," (one of the oldest forms of Korean popular music) which are preferred by lower-educated and older individuals, suggesting that the more ``cosmopolitan'' omnivores still engage in patterns of symbolic exclusion directed at older persons of lower educational status \citep[321]{kim2020anything-71b}.

@@

\section*{Data}
The data for this study come from three rounds of survey data collection on Americans' cultural tastes. The two waves of data collection yielded two convenience samples: one collected in 2021 and the other in 2023, with an oversample of people with advanced educational degrees. Both of these samples come from the Prolific Academic (ProA) platform. Prolific has emerged as a preferred alternative to Amazon’s Mechanical Turk for researchers seeking high-quality, suitably motivated participant pools. Unlike MTurk, ProA was explicitly designed with social-scientific researchers in mind and offers a high-quality, better-compensated participant pool. Also, unlike MTurk, ProA mandates a minimum payment based on the expected time required to complete the task. Participants in our study were compensated at a rate of \$9.50 per hour, which ProA indicates as a “good” compensation rate. The main participant pool for this study on the Prolific platform was limited to participants between the ages of eighteen and eighty-five who reside in the United States and whose first language is English (or are fluent in English). The study was also restricted to participants who scored at or above 95\% on ProA’s ``approval rate'' (the proportion of times a participant’s study response has been accepted in other studies as adequate). Survey completion was verified by embedding a completion code as the last question, which participants had to input on the Prolific website to confirm they had read and completed each survey question.

@@

\section*{Results}
\subsection*{Probability of Dislikes by Genre}
Table~\ref{tab:dis-by-genres} shows the probability of any genre experiencing a judgment of dislike for both the Prolific and Lucid samples, pooling the 2021 and 2023 Prolific samples. As we can see, Metal is the genre most likely to be disliked in both samples, consistent with previous work on Americans' musical tastes based on data collected earlier \citep{bryson1996anything-311, lizardo2015musical-8c6}. Both samples also agree that the two genres least likely to be disliked are Rock and Pop music. There is some disagreement across samples on the exact ranking of other genres. Country music experiences the most significant disparity, ranking second among the most disliked genres in the Prolific sample but near the bottom in the Lucid sample. Beyond that, both datasets agree that Musicals, Rap, and Disco are at the top of the dislike list, while Classical, R\&B, and Jazz are closer to the bottom.

@@

\subsection*{Socio-Demographic Distribution of Categorical Tolerance}
\begin{figure}[ht!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-pol.png}
            \caption{Political Ideology}
            \label{fig:cat-tol-pol}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-edu.png}
            \caption{Education}
            \label{fig:cat-tol-edu}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-inc.png}
            \caption{Income}
            \label{fig:cat-tol-inc}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-age.png}
            \caption{Age}
            \label{fig:cat-tol-age}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-rac.png}
            \caption{Ethnoracial Identification}
            \label{fig:cat-tol-rac}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-gen.png}
            \caption{Gender Identification}
            \label{fig:cat-tol-gen}
    \end{subfigure}
    \caption{Proportion of Categorical Tolerants across different socio-demographic characteristics.}
    \label{fig:cat-tol}
\end{figure}

Figure~\ref{fig:cat-tol} shows how the sample probability of being a categorical tolerant is distributed among various socio-demographic categories. Each panel of Figure~\ref{fig:cat-tol} shows a ``lollipop plot'' with the numerical axis being the proportion of categorical tolerants at each level of the corresponding socio-demographic covariate. The red dashed reference line is the observed sample proportion of categorical tolerants.

As Figure~\ref{fig:cat-tol-age} shows, age is the most straightforward factor structuring categorical tolerance, replicating the pattern observed by \citet{lizardo2016end-4fb}: Younger people are more likely to be categorical tolerants compared to older people, who are strongly under-represented among categorical tolerants; accordingly, the probability of being a categorical tolerant in these data is maximized among younger adults (individuals in their thirties), suggesting that very young people are induced to use musical genres for purposes of symbolic inclusion to a greater extent than people at this life-stage. Regardless, it is clear that if cohort replacement dynamics drive the rise of categorical tolerance, then we should expect it to remain a fixture of the cultural taste landscape in the U.S. as older, less categorically tolerant cohorts exit the population.

The other obvious factor structuring categorical tolerance in the United States is race. Mirroring L\&S's earlier findings, Figure~\ref{fig:cat-tol-rac} shows that categorical tolerance continues to be primarily a non-white phenomenon, with whites (and to a similar extent respondents who identify as Hispanic) under-represented among categorical tolerants, and Black, Asian, and Native American respondents over-represented. Also similar to L\&S's findings, the traditional Bourdieusian structuring factors (e.g., education and income) do not have a straightforward link to categorical tolerance, with both showing non-linear patterns (categorical tolerants over-represented among both high and low education and high and low-income respondents).

Nevertheless, the apparent over-representation of the most highly educated stratum among the categorically tolerant suggests an elite move in this direction, which was not evident in L\&S's previous analysis, which mainly pointed to cohort/age and ethnoracial status effects. Interestingly, we also observe a strong gender effect---unlike L\&S's earlier findings---which suggests a relatively large gender gap in the categorical tolerance taste pattern, with men overrepresented and women underrepresented among the ranks of categorical tolerants. Finally, categorical tolerance---in contrast to symbolic exclusion as we will see in a bit---is not polarized along political-ideological lines, with no clear pattern shown according to conservative/liberal placement.

@@

Symbolic exclusion tendencies among different groups can be straightforwardly attributed to age and education, with older, less educated respondents expressing more dislikes than younger, more educated ones. Importantly, symbolic exclusion is also structured by political ideology in the expected direction---see \citet{rawlings2023polarization-0af}---with liberals being less likely to express cultural dislikes than self-identified conservatives. In the same way, non-whites in the sample are less likely to express cultural dislikes (compared to white respondents), while women express more dislikes (compared to those who identify as men).

\subsection*{Multivariable Analysis Results}
In their original paper, \citet{lizardo2016end-4fb} proposed modeling categorical tolerance and symbolic exclusion jointly as a hurdle process. The basic idea is that categorical tolerants are a distinct slice of the population who are not at risk of engaging in symbolic exclusion (expressing dislikes). Thus, we can statistically model the joint predictors of both tendencies by assuming that there is a set of predictors that drive the probability of being in the categorical tolerant group (thus not being at risk of expressing dislikes), and net of this, there is a second set of predictors that drive the number of dislikes expressed for those who are at risk of doing so. The zero-inflated Poisson model is thus a natural statistical framework for modeling this dual regime data-generating process \citep{zorn1998analytic-6b1}. Since the univariate distribution of cultural dislikes is comparable across samples (see ~\ref{tab:dis-dist}), I pool the three samples to increase statistical power and report results from the pooled sample analysis, including a binary indicator for each survey sample (using the 2021 Prolific sample as the reference category) in each model. I use listwise deletion of cases with missing values for the socio-demographic covariates included in the model, which leaves us with a total analytical sample of $N = 2291$.

>>>>

\newpage
\begin{abstract}
This paper updates the empirical picture of Categorical Tolerance (CT), namely, the pattern of refusing to report dislikes across cultural genres, in the United States during the third decade of the twenty-first century. Analyzing recent survey data from two platforms, I find that CT has continued its march among Americans, reaching approximately 20\% of respondents. The analysis confirms earlier-observed demographic trends, showing that CT is strongly associated with younger cohorts and non-white individuals. However, I also find that individuals reporting the highest educational attainment are now overrepresented among categorical tolerants, suggesting that CT may increasingly function as an elite cultural strategy consistent with contemporary forms of status display, signaling openness and refusal to refuse. Furthermore, the study uses political ideology as a predictor of symbolic exclusion, revealing that while the odds of being a CT itself are not strongly polarized, the inclination toward symbolic exclusion among non-CTs is, with conservatives significantly more likely to express a greater volume of cultural dislikes than liberals. This result shows that political ideology, alongside age and race, is a central determinant of cultural exclusion in the contemporary context. 
\end{abstract}
\newpage
\section*{Introduction}
Ever since Richard Peterson introduced the felicitous term ``patterns of cultural choice'' into sociological discourse more than four decades ago \citep{peterson1983patterns-f85}, sociologists have been busy empirically uncovering and debating the sociological reality, drivers, and correlates of various such patterns. These include, most famously and influentially, the Petersonian cultural \textit{omnivore} \citep{peterson1996changing-967, goldberg2011mapping-77a, warde2008omnivorous-e77} along with their evil twin the culturally exclusive \textit{univore} \citep{bryson1997what-933, peterson1992understanding-ce3, tonkovi2025globallocal-96f}, but also culturally \textit{voracious} consumers \citep{sullivan2007omnivore-018}, \textit{poly-purists} and \textit{poly-mixers} \citep{goldberg2016what-4e3, poecke2018pure-873}, \textit{decisives} and \textit{indecisives} \citep{sonnett2004musical-961}, and even plain old \textit{snobs} engaging in (presumably) Bourdieusian boundary-drawing distinction \citep{atkinson2011context-d44, nault2021social-1bf}, among many others.

@@

Why are dislikes expressed in social surveys on cultural tastes important? As \citet{bourdieu1984distinction-835} himself noted, taste is often asserted negatively through refusal (p. 56). \citet{bryson1996anything-311} linked this dynamic to the idea of ``symbolic exclusion'' or the \textit{indirect} action of drawing a symbolic (social) boundary against particular (usually lower status) groups by distancing oneself from the cultural objects that those groups are perceived to consume \citep{lizardo2016cultural-aaa}. This recognition has led scholars to stress the critical importance of studying ``dislikes" alongside ``likes" to fully comprehend the dynamics of symbolic exclusion and the construction of cultural boundaries \citep{lizardo2015musical-8c6, lindblom2022growing-ded, oncini2023cultural-323}. This general framework has proven helpful for understanding social and cultural dynamics, even beyond the United States. For example, a recent study of musical taste conducted in South Korea found that tolerant omnivores still excluded genres like ``gugak" (Korean traditional music) and ``trot," (one of the oldest forms of Korean popular music) which are preferred by lower-educated and older individuals, suggesting that the more ``cosmopolitan'' omnivores still engage in patterns of symbolic exclusion directed at older persons of lower educational status \citep[321]{kim2020anything-71b}.

@@

\section*{Data}
The data for this study come from three rounds of survey data collection on Americans' cultural tastes. The two waves of data collection yielded two convenience samples: one collected in 2021 and the other in 2023, with an oversample of people with advanced educational degrees. Both of these samples come from the Prolific Academic (ProA) platform. Prolific has emerged as a preferred alternative to Amazon’s Mechanical Turk for researchers seeking high-quality, suitably motivated participant pools. Unlike MTurk, ProA was explicitly designed for social-scientific researchers and offers a high-quality, better-compensated participant pool. Also, unlike MTurk, ProA mandates a minimum payment based on the expected time required to complete the task. Participants in our study were compensated at a rate of \$9.50 per hour, which ProA indicates as a “good” compensation rate. The main participant pool for this study on the Prolific platform was limited to participants between the ages of eighteen and eighty-five who reside in the United States and whose first language is English (or are fluent in English). The study was also restricted to participants who scored at or above 95\% on ProA’s ``approval rate'' (the proportion of times a participant’s study response has been accepted in other studies as adequate). Survey completion was verified by embedding a completion code as the last question, which participants had to input on the Prolific website to confirm they had read and completed each survey question.

@@

\section*{Results}
\subsection*{Probability of Dislikes by Genre}
Table~\ref{tab:dis-by-genres} shows the probability of any genre experiencing a judgment of dislike for both the Prolific and Lucid samples, pooling the 2021 and 2023 Prolific samples. As we can see, Metal is the genre most likely to be disliked in both samples, consistent with previous work on Americans' musical tastes based on earlier data \citep{bryson1996anything-311, lizardo2015musical-8c6}. Both samples also agree that the two genres least likely to be disliked are Rock and Pop music. There is some disagreement across samples on the exact ranking of other genres. Country music experiences the most significant disparity, ranking second among the most disliked genres in the Prolific sample but near the bottom in the Lucid sample. Beyond that, both datasets agree that Musicals, Rap, and Disco are at the top of the dislike list, while Classical, R\&B, and Jazz are closer to the bottom.

@@

One worry, however, is that the differences between the percentages of categorical tolerants observed here and those in L\&S's original study are a simple function of the fact that the previous study used a larger number of genres than this one, thus exposing people to the ``risk'' of disliking more options. As a robustness check, I compared the distribution of dislikes in the current sample with that in L\&S's original study. While most of the abstract genre labels used in the two studies can be matched without a problem, two discrepancies need to be reconciled. First, the current research includes ``Disco'' as a genre, one that was absent from the original L\&S study. Accordingly, I drop this genre, leaving us with 11 comparable genres. The other issue is that, while the current research asks only about likes and dislikes for "Rock," L\&S's previous study disaggregated this category into three subgenres: Classic, Contemporary, and Alternative. Accordingly, I merge these three categories in L\&S's original data into an omnibus ``Rock'' category, treating a dislike of any of them as a dislike of Rock. Finally, to compare apples to apples, I use only the more representative data collected in 2025 as a comparison point, as L\&S's data also came from a similar sample weighted to match 2010 census demographics in terms of age, race, and education.

\begin{figure}[ht!]
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-comp.png}
    \caption{Univariate plot of number of dislikes, joint Prolific and Lucid samples (N = 2367).}
    \label{fig:main-comp}
\end{figure}

With these caveats in mind, Figure~\ref{fig:main-comp} shows the univariate distribution in L\&S's original data against the 2025 Cint sample for the eleven matched genres. We can see that the estimated descriptive proportion of categorical tolerants is a bit higher than the number reported by L\&S with the reduced number of genres (about 17\%), suggesting that \textit{some} of the observed differences may be due to this methodological artifact. However, note that the proportion of categorical tolerants is still significantly higher in the more recent data with the eleven matched genres (about 21\%), with a Kolmogorov-Smirnov test rejecting the null hypothesis that the two samples are drawn from the same univariate distribution ($D = 0.09, p < 0.001$), suggesting that the distribution of dislikes has indeed shifted since 2012. ``Eyeballing'' Figure~\ref{fig:main-comp} invites the inference that if there has indeed been such a shift, it is mainly concentrated in the estimated number of categorical tolerants.

Nevertheless, the \textit{descriptive} proportion of persons with zero dislikes is not a strict estimate of the number of categorical tolerants, since these include a mixture of ``structural zeros'' (true categorical tolerants) and ``random zeros'' (people at risk of disliking but who did not). To tease this out, and provide a more formal test of the differences between the 2012 and 2025 distributions of dislikes, I fit a zero-inflated Poisson model to the pooled 2012/2025 data (see below for a more detailed justification of this statistical approach), with a single predictor in both the ``count'' and ``zero-inflation'' part of the model: An indicator variable that equals one for observations in the 2025 sample and zero otherwise. The results are shown in Table~\ref{tab:comp-zip}.

\begin{figure}[ht!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
    \captionsetup[subfloat]{labelformat=simple}
      \renewcommand{\thesubfigure}{Table 3(a)}% New fixed/manual numbering
     \begin{subfigure}[b]{0.3\textwidth}
    \includegraphics[trim={0 50cm 0 0},clip, width=5.0\textwidth]{Tabs/zinf-reg-comp.png}
            \caption{}
            \label{tab:comp-zip}
    \end{subfigure} 
    \hspace{2cm}
      \renewcommand{\thesubfigure}{Figure 3(b)}% New fixed/manual numbering
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/zip-pred-comp.png}
            \caption{}
            \label{fig:comp-pred}
    \end{subfigure}
    \caption*{}
    \label{fig:comp}
\end{figure}

The single coefficient estimate in the ``count'' part of the model in Table~\ref{tab:comp-zip} tests the hypothesis that the differences between the two distributions are due to the non-zero counts. This hypothesis is not supported by the data ($\beta_{2025} = -0.01, p = 0.61$). The single coefficient estimate in the ``inflation'' part of the model tests the hypothesis that the main difference between the two distributions is the larger excess zeros observed in 2025. This hypothesis is supported by the data ($\beta_{2025} = 0.26, p < 0.05$). Furthermore, the predicted probabilities from this model can thus give us a more precise estimate of the different representations of ``true'' categorical tolerants across the two samples.\footnote{Estimated using the \texttt{ggeffects} packages in \textit{R}.} These are shown in Figure~\ref{fig:comp-pred}. As we can see the estimated number of categorical tolerants from the model in Table~\ref{tab:comp-zip} for 2012 is close to that reported in L\&S's original paper: About 15\%. The number of categorical tolerants estimated in the 2025 Cint sample, however, is significantly larger, at just under 19\%.

\subsection*{Socio-Demographic Distribution of Categorical Tolerance}
Figure~\ref{fig:cat-tol} shows how the sample probability of being a categorical tolerant is distributed among various socio-demographic categories. Each panel of Figure~\ref{fig:cat-tol} shows a ``lollipop plot'' with the numerical axis being the proportion of categorical tolerants at each level of the corresponding socio-demographic covariates. The red-dashed reference line shows the observed proportion of categorical tolerants in the sample.

As Figure~\ref{fig:cat-tol-age} shows, age is the most straightforward factor structuring categorical tolerance, replicating the pattern observed by \citet{lizardo2016end-4fb}: Younger people are more likely to be categorical tolerants compared to older people, who are strongly under-represented among categorical tolerants; accordingly, the probability of being a categorical tolerant in these data is maximized among younger adults (individuals in their thirties), suggesting that very young people are induced to use musical genres for purposes of symbolic inclusion to a greater extent than people at this life-stage. Regardless, it is clear that if cohort replacement dynamics drive the rise of categorical tolerance, we should expect it to remain a fixture of the U.S. cultural taste landscape as older, less categorically tolerant cohorts exit the population.

\begin{figure}[ht!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-pol.png}
            \caption{Political Ideology}
            \label{fig:cat-tol-pol}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-edu.png}
            \caption{Education}
            \label{fig:cat-tol-edu}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-inc.png}
            \caption{Income}
            \label{fig:cat-tol-inc}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-age.png}
            \caption{Age}
            \label{fig:cat-tol-age}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-rac.png}
            \caption{Ethnoracial Identification}
            \label{fig:cat-tol-rac}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-gen.png}
            \caption{Gender Identification}
            \label{fig:cat-tol-gen}
    \end{subfigure}
    \caption{Proportion of Categorical Tolerants across different socio-demographic characteristics.}
    \label{fig:cat-tol}
\end{figure}

The other obvious factor structuring categorical tolerance in the United States is race. Mirroring L\&S's earlier findings, Figure~\ref{fig:cat-tol-rac} shows that categorical tolerance continues to be primarily a non-white phenomenon, with whites (and to a similar extent respondents who identify as Hispanic) under-represented among categorical tolerants, and Black, Asian, and Native American respondents over-represented. Also in line with L\&S's findings, the traditional Bourdieusian structuring factors (e.g., education and income) do not have a straightforward link to categorical tolerance, with both showing non-linear patterns (categorical tolerants over-represented among both high- and low-education and high- and low-income respondents).

Nevertheless, the apparent over-representation of the most highly educated stratum among the categorically tolerant suggests an elite move in this direction, which was not evident in L\&S's previous analysis, which mainly pointed to cohort/age and ethnoracial status effects. Interestingly, we also observe a strong gender effect---unlike L\&S's earlier findings--- suggesting a relatively large gender gap in the categorical tolerance taste pattern, with men overrepresented and women underrepresented among categorical tolerants. Finally, categorical tolerance---in contrast to symbolic exclusion, as we will see in a bit---is not polarized along political-ideological lines, with no clear pattern by conservative/liberal placement.

@@

Symbolic exclusion tendencies across groups can be straightforwardly attributed to age and education, with older, less educated respondents expressing more dislike than younger, more educated ones. Importantly, symbolic exclusion is also structured by political ideology in the expected direction---see \citet{rawlings2023polarization-0af}---with liberals being less likely to express cultural dislikes than self-identified conservatives. In the same way, non-whites in the sample are less likely to express cultural dislikes (compared to white respondents), while women express more dislikes (compared to those who identify as men).

\subsection*{Multivariable Analysis Results} \label{sec:multvariable}
In their original paper, \citet{lizardo2016end-4fb} proposed modeling categorical tolerance and symbolic exclusion jointly as a hurdle process. The basic idea is that categorical tolerants are a distinct slice of the population who are not at risk of engaging in symbolic exclusion (expressing dislikes). Thus, we can statistically model the joint predictors of both tendencies by assuming that there is a set of predictors that drive the probability of being in the categorical tolerant group (thus not being at risk of expressing dislikes), and net of this, there is a second set of predictors that drive the number of dislikes expressed for those who are at risk of doing so. The zero-inflated Poisson model is thus a natural statistical framework for modeling this dual regime data-generating process \citep{zorn1998analytic-6b1}. Since the univariate distribution of cultural dislikes is comparable across samples (see ~\ref{tab:dis-dist}), I pool the three samples to increase statistical power and report results from the pooled sample analysis, including a binary indicator for each survey sample (using the 2021 Prolific sample as the reference category) in each model. I use listwise deletion of cases with missing values for the socio-demographic covariates included in the model, which leaves us with a total analytical sample of $N = 2291$.
